Adapting the MVDR to a GPU for active sonar systems of different sizes.

### 2013-01-22 ASA2013/asa2013.tex
la2pdf commit - 2013:01:22	18:42:31	(Tue22.Jan)

Through a case study of on such technique, the Minimum Variance Distortionless Response (MVDR) beamformer, we identify these challenges and explain how they were overcome. The MVDR is a technique that displays a notable potential for improving image quality over simple conventional methods, but is far more computationally complex. This is because a spatial covariance matrix must be estimated and inverted for each image pixel. For systems with less than 20-30 channels the estimation step dominates, while the inversion step   %Unlike other studies, w While most studies tend to focus on reducing the dimensionality of the convariance matrix to

>>>>

Through a case study of on such technique, the Minimum Variance Distortionless Response (MVDR) beamformer, we identify these challenges and explain how they were overcome. The MVDR technique displays a notable potential for improving image quality over simple conventional methods, but is far more computationally complex. This is because a spatial covariance matrix must be estimated and inverted for each image pixel. These steps take turn in being the most complex depending on system size. With less than 20-30 channels the algorithm spends most of its time with the estimation step, while at larger system sizes the inversion step completely dominates. For large systems one should try to bypass the estimation/inversion step altogether.

Therefore we suggest two different approaches for     dominates the computation time, while for larger system sizes the the inversion step   %Unlike other studies, w While most studies tend to focus on reducing the dimensionality of the convariance matrix to
